### 2021-05-15 code/manuscript.Rmd
updated freq models to all_fit

  We have no conflict of interest to disclose.
  The preprocessed data and code for this study are openly available at https://osf.io/uksbc/.
abstract: |
  Does our perception of an object change as soon as we discover what function it serves? This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities. In this experiment, we showed participants (*n* = 24) pictures of 120 unfamiliar objects either together with matching information about their function---leading to semantically informed perception---or together with non-matching information---resulting in naive perception. We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another. We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component and reduced amplitudes in the N400 component. When the same objects were presented once more (without any information), the N400 effect persisted and we now also observed enlarged amplitudes in the P1 component in response to objects for which semantically informed perception had taken place. We replicated these novel findings in an independent sample (*n* = 24). Consistent with previous work, these results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).

keywords          : "objects, semantic knowledge, visual perception, event-related potentials"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
bibliography      : "misc/bibliography.bib"
csl               : "misc/apa.csl"
zotero            : "aha"
documentclass     : "apa7"
classoption       : "man"
output            :
  papaja::apa6_pdf:
    latex_engine  : "xelatex"
editor_options: 
  chunk_output_type: console
header-includes:
  - \geometry{a4paper}
  - \fancyheadoffset[R,L]{0pt}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage[bottom]{footmisc}
  - \interfootnotelinepenalty=10000
  - \usepackage{setspace}
  - \AtBeginEnvironment{tabular}{\doublespacing}
  - \usepackage{makecell}
  - \renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1.5}}
---

```{r setup, include=FALSE}
# Load packages
library(lmerTest)
library(emmeans)
library(papaja)
library(reticulate)
library(tidyverse)
library(magrittr)
library(cowplot)

@@

# Re-run preprocessing and/or model fitting?
rerun_preprocessing <- TRUE
rerun_model_fitting <- TRUE

# File names for easier I/O
fnames <- list(
  montage = "data/processed/montage.csv",
  evo_gavg = "data/processed/evo_gavg.csv",
  evo_tfr_gavg = "data/processed/evo-tfr_gavg.csv",
  evo_tfr_diff = "data/processed/evo-tfr_diff.csv",
  evo_tfr_gavg_nochans = "data/processed/evo-tfr_gavg-nochans.csv",
  evo_tfr_diff_nochans = "data/processed/evo-tfr_diff-nochans.csv"
)
```

@@

  # Get standard EasyCap electrode positions and project them into 2D space
  read_csv("data/preprocessed/sub-01_tfr-evo.csv", col_types = cols()) %>%
    select(-c(part, condition, subject_id, time, freq)) %>%
    colnames() -> ch_names
  import("mne.channels._standard_montage_utils")$MONTAGE_PATH %>%
    paste0("/easycap-M1.txt") %>%
    read_tsv(col_types = cols()) %>%
    rename(electrode = Site) %>%
    inner_join(tibble(electrode = ch_names), ., by = "electrode") %>%
    mutate(
      x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
      y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
    ) %>%
    mutate(across(c(x, y), round, 3)) %>%
    write_csv(fnames$montage)
}
```

```{python, grand_averaging, eval=rerun_preproc}
from os import makedirs

@@

# Average first across subjects, then across electrodes
id_vars.remove("subject_id")
fnames = [r.fnames["evo_tfr_gavg"], r.fnames["evo_tfr_diff"]]
fnames_nochans = [r.fnames["evo_tfr_gavg_nochans"], r.fnames["evo_tfr_diff_nochans"]]
for df, fname, fname_nochans in zip([evo_tfr, evo_tfr_diff], fnames, fnames_nochans):
    df = df.groupby(id_vars, as_index=False).mean()
    df.to_csv(fname, float_format="%.3f", index=False)
    df["power"] = df[electrodes].mean(axis=1)
    df.drop(electrodes, axis=1, inplace=True)
    df.to_csv(fname_nochans, float_format="%.3f", index=False)
del df, evo_tfr, evo_tfr_diff
```

```{r, tfr_wip}
please_stop_here()

# Read evoked power
paste0("data/preprocessed/", subject_id, "_tfr-evo.csv") %>%
  map(read_csv, col_types = cols())

  map2(subject_id, function(fname, id) {
    read_csv(fname, col_types = cols(), progress = FALSE) %>%
      mutate(participant = id)
  }) %>%
  bind_rows() -> evo

# Average across participants
grouping <- c("part", "condition", "time", "freq")
evo %<>%
  group_by(across(all_of(grouping))) %>%
  summarise(across(-participant, .fns = mean), .groups = "drop")

# Average across channels
evo %>%
  pivot_longer(!all_of(grouping), names_to = "channel", values_to = "power") %>%
  group_by(across(all_of(grouping))) %>%
  summarise(power = mean(power), .groups = "drop") -> evo_all_channels

# Average across conditions within parts
evo_all_channels %>%
  group_by(part, time, freq) %>%
  summarise(power = mean(power), .groups = "drop") -> evo_all_channels_conds

# Plot
evo_all_channels_conds %>%
  ggplot(aes(x = time, y = freq, fill = power)) +
  facet_wrap(~part) +
  geom_raster() +
  scale_fill_viridis_c(limits = c(0, 2), oob = scales::squish) +
  annotate("rect", xmin = 150, xmax = 400, ymin = 30, ymax = 50, color = "white", fill = NA) +
  theme(aspect.ratio = 0.5) +
  theme_minimal() +
  coord_cartesian(expand = FALSE) +
  ggsave("evo_all_channels_conds.pdf", width = 7, height = 2)

# Compute differences between conditions
evo_all_channels %>%
  group_by(part, time, freq) %>%
  mutate(power = power - power[condition == "Naive"]) %>%
  filter(condition == "Informed") %>%
  ggplot(aes(x = time, y = freq, fill = power)) +
  facet_wrap(~part) +
  geom_raster() +
  scale_fill_viridis_c(limits = c(0, 1), oob = scales::squish) +
  annotate("rect", xmin = 150, xmax = 400, ymin = 30, ymax = 50, color = "white", fill = NA) +
  theme(aspect.ratio = 0.5) +
  theme_minimal() +
  coord_cartesian(expand = FALSE) +
  ggsave("evo_all_channels_diff.pdf", width = 7, height = 2)
```

```{r, models_freq}
# Read single trial data for all subjects
paste0("data/preprocessed/", subject_id, "_trials.csv") %>%
  map(read_csv, col_types = cols()) %>%
  bind_rows() %>%
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c("Informed", "Naive")),
    subject_id = factor(subject_id),
    item_id = factor(item_id)
  ) %>%
  na.omit() -> trials

contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1)))
contrasts_part <- t(cbind(
  c("I" = -1, "II" = 1, "III" = 0),
  c("I" = 0, "II" = -1, "III" = 1)
))

# Apply these contrasts to the factors in the data
contrasts(trials$condition) <- MASS::ginv(contrasts_condition)
contrasts(trials$part) <- MASS::ginv(contrasts_part)

formula <- N400 ~ part / condition + (1|subject_id) + (1|item_id)
mod <- lmer(formula, data = trials)
summary(mod)

# Remove any trials excluded from conditions
aha %>%
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> aha

# Define contrast coding for condition (informed-naive) and part (2-1, 3-1)
contrasts_condition <- t(cbind(
  c("Informed" = 1, "Naive" = -1)
))
contrasts_part <- t(cbind(
  c("I" = -1, "II" = 1, "III" = 0),
  c("I" = 0, "II" = -1, "III" = 1)
))

# Apply these contrasts to the factors in the data
contrasts(aha$condition) <- MASS::ginv(contrasts_condition)
contrasts(aha$part) <- MASS::ginv(contrasts_part)

# Specify model formula
form <- erp ~ part * condition +
  (part * condition | participant) +
  (part * condition | item)

# Specify follow-up comparisons
specs <- pairwise ~ condition | part

# Calculate linear mixed-effects models and follow-up comparisons
map(comps$name, function(comp, formula = form, data = aha, specs = specs) {
  data %<>% rename(erp = all_of(comp))
  mod <- lmer(formula, data, all_fit = TRUE)
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  em <- emmeans(mod, specs = specs, infer = TRUE, data = data)
  modlist <- list(
    model = mod,
    anova = anova(mod),
    summary = summary(mod),
    means = as.data.frame(em$means),
    contrasts = as.data.frame(em$contrasts)
  )
}) %>%
  set_names(comps$name) %T>%
  saveRDS(fnames$models_freq) -> mods_freq
```

@@

contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1)))
contrasts_part <- t(cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)))
contrasts(data_brm$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_brm$part) <- MASS::ginv(contrasts_part)

@@

```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
# Load montage and data
montage <- read_csv(fnames$montage, col_types = cols())
evokeds <- read_csv(fnames$evo_gavg, col_types = cols())

# Create plot for Experiment 1
plot_grid(
  plot_trials(),
  plot_erps(comps = comps, evokeds = evokeds_exp1, models = models_exp1, montage = montage),
  nrow = 2, rel_heights = c(5, 6), labels = c("A", "B"), label_fontfamily = "Helvetica"
) + # Add some lines (to separate the parts) and the legend
  annotate(geom = "segment", x = 0.328, xend = 0.328, y = -Inf, yend = 0.53, linetype = "dashed") +
  annotate(geom = "segment", x = 0.672, xend = 0.672, y = -Inf, yend = 0.53, linetype = "dashed") +
  annotate(geom = "segment", x = 0.328, xend = 0.28, y = 0.53, yend = 0.58, linetype = "dashed") +
  annotate(geom = "segment", x = 0.672, xend = 0.72, y = 0.53, yend = 0.58, linetype = "dashed") +  
  annotate(geom = "segment", x = 0.28, xend = 0.28, y = 0.58, yend = Inf, linetype = "dashed") +
  annotate(geom = "segment", x = 0.72, xend = 0.72, y = 0.58, yend = Inf, linetype = "dashed") +
  draw_plot(plot_legends_erps(direction = "vertical"), x = 0.405, y = 0.422, width = 1, height = 1)
```

(ref:figure-1-caption) Procedure and Results of Experiment 1\smallskip

@@

Offline, the data were preprocessed using the MNE software [Version 0.21.0\; @gramfort2013] in Python [Version 3.8.5\; @vanrossum2009]. First, all scalp electrodes were re-referenced to the common average. Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA). The first 15 components were extracted by the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz. Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the *find\_bads\_eog* function. After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied. Next, the continuous EEG was epoched into segments of 2 s, starting 500 ms before the onset of the visual presentation of each unfamiliar object. The epochs were baseline-corrected by subtracting the average voltage during the 200 ms before stimulus onset. Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis. This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp1)/360, accuracy = 0.1)`; range `r min(rejected_exp1)` to `r max(rejected_exp1)` trials). Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (for the positions of these electrodes on the scalp, see the topographies in Figure \@ref(fig:exp1-plot)B).

@@

First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded objects from all further analyses when participants classified them as being known in the pre-insight part (i.e., before any keywords were presented). This led to the exclusion of an average of `r format(round(objects_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects). Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analysis was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A). Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption. This was the case for an average of `r format(round(objects_exp1["Informed"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords). Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption. This was the case for an average of `r format(round(objects_exp1["Naive"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords). Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts. This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any down-stream effects on the subsequent perception of the objects (post-insight part).

@@

@@

# Apply contrasts to the factors in the data
contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_exp2$part) <- MASS::ginv(contrasts_part)

@@

```{r exp2-plot, include=TRUE, fig.height=7.5, fig.cap = "(ref:figure-2-caption)"}
# Create plot for Experiment 2
plot_grid(
  #plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
  plot_headings(spacing = c(10, 1, 10, 1, 10)),
  plot_erps(comps = comps, evokeds = evokeds_exp2, models = models_exp2, montage = montage),
  plot_legends_erps(direction = "horizontal"),
  nrow = 3, rel_heights = c(0.3, 6, 1.2), labels = NULL
) + # Add some lines (to separate the parts)
  annotate(geom = "segment", x = 0.328, xend = 0.328, y = 0.15, yend = Inf, linetype = "dashed") +
  annotate(geom = "segment", x = 0.672, xend = 0.672, y = 0.15, yend = Inf, linetype = "dashed")
```

(ref:figure-2-caption) Results of Experiment 2\smallskip

@@

(ref:figure-3-caption) Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip

>>>>

  We have no conflict of interest to disclose.
  The preprocessed data and code for this study are openly available at https://osf.io/uksbc/.
abstract: |
  Does our perception of an object change as soon as we discover what function it serves? This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities. In this experiment, we showed participants (*n* = 24) pictures of 120 unfamiliar objects either together with matching information about their function---leading to semantically informed perception---or together with non-matching information---resulting in naive perception. We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another. We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component and reduced amplitudes in the N400 component. When the same objects were presented once more (without any information), the N400 effect persisted and we now also observed enlarged amplitudes in the P1 component in response to objects for which semantically informed perception had taken place. We replicated these novel findings in an independent sample (*n* = 24). Consistent with previous work, these results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
keywords          : "objects, semantic knowledge, visual perception, event-related potentials"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
bibliography      : "misc/bibliography.bib"
csl               : "misc/apa.csl"
zotero            : "aha"
documentclass     : "apa7"
classoption       : "man"
output            :
  papaja::apa6_pdf:
    latex_engine  : "xelatex"
editor_options: 
  chunk_output_type: console
header-includes:
  - \geometry{a4paper}
  - \fancyheadoffset[R,L]{0pt}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage[bottom]{footmisc}
  - \interfootnotelinepenalty=10000
  - \usepackage{setspace}
  - \AtBeginEnvironment{tabular}{\doublespacing}
  - \usepackage{makecell}
  - \renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1.5}}
---

```{r setup, include=FALSE}
# Load packages
library(emmeans)
library(MASS)
library(afex)
library(reticulate)
library(papaja)
library(cowplot)
library(scales)
library(tidyverse)
library(magrittr)
library(furrr)

@@

# Re-run preprocessing and/or model fitting?
rerun_preprocessing <- FALSE
rerun_model_fitting <- TRUE

# File names for easier I/O
fnames <- list(
  montage = "data/processed/montage.csv",
  objects_per_condition = "data/processed/obj-per-cond.csv",
  evo_gavg = "data/processed/evo_gavg.csv",
  evo_tfr_flat = "data/processed/evo-tfr_flat.csv",
  evo_tfr_diff = "data/processed/evo-tfr_diff.csv",
  evo_tfr_flat_nochans = "data/processed/evo-tfr_flat-nochans.csv",
  evo_tfr_diff_nochans = "data/processed/evo-tfr_diff-nochans.csv",
  models_freq = "data/processed/models_freq.RDS"
)
```

@@

  # Get standard EasyCap electrode positions and project them into 2D space
  dir.create("data/processed")
  read_csv("data/preprocessed/sub-01_tfr-evo.csv", col_types = cols()) %>%
    select(-c(part, condition, subject_id, time, freq)) %>%
    colnames() -> ch_names
  import("mne.channels._standard_montage_utils")$MONTAGE_PATH %>%
    paste0("/easycap-M1.txt") %>%
    read_tsv(col_types = cols()) %>%
    rename(electrode = Site) %>%
    inner_join(tibble(electrode = ch_names), ., by = "electrode") %>%
    mutate(
      x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
      y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
    ) %>%
    mutate(across(c(x, y), round, 3)) %>%
    write_csv(fnames$montage)

  # Determine number of objects per condition for each participant
  fname_log %>%
    map2(subject_id, pp$read_log) %>%
    bind_rows() %>%
    with(table(subject_id, condition) / 3) %>%
    as.data.frame.matrix() %>%
    rownames_to_column("subject_id") %>%
    write_csv(fnames$objects_per_condition)
}
```

```{python, grand_averaging, eval=TRUE}
from os import makedirs

@@

# Compute flat average across conditions
id_vars.remove("condition")
evo_tfr_flat = evo_tfr.groupby(id_vars, as_index=False).mean()

# Average across subjects and save
id_vars.remove("subject_id")
dfs = [evo_tfr_flat, evo_tfr_diff]
fnames_tfr = [r.fnames["evo_tfr_flat"], r.fnames["evo_tfr_diff"]]
for df, fname in zip(dfs, fnames_tfr):
    df = df.groupby(id_vars, as_index=False).mean()
    df.to_csv(fname, float_format="%.3f", index=False)
del df, dfs, evo, evo_tfr, evo_tfr_diff, evo_tfr_flat
```

```{r, models_freq}
# Read single trial data for all subjects
paste0("data/preprocessed/", subject_id, "_trials.csv") %>%
  map(read_csv, col_types = cols()) %>%
  bind_rows() %>%
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c("Informed", "Naive")),
    subject_id = factor(subject_id),
    item_id = factor(item_id),
    RT = ifelse(RT < 200, NA, RT),
    logRT = log(RT)
  ) -> trials

# Remove trials with unrealistically short RTs or invalid conditions
sum(is.na(trials$RT))
sum(is.na(trials$RT)) / nrow(trials)
trials %<>% na.omit()

# Contrast coding for parts
cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)) %>%
  t() %>%
  ginv() -> contrasts(trials$part)

# Contrast coding for conditions
c("Informed" = 1, "Naive" = -1) %>%
  t() %>%
  ginv() -> contrasts(trials$condition)

# Load fitted models or rerun them
if (!rerun_model_fitting) {

  # Load models
  models_freq <- readRDS(fnames$models_freq)
} else {

  # Compute models for dependent variables in parallel
  dvs <- c("logRT", "P1", "N170", "N400")
  n_cores <- min(length(dvs), availableCores())
  plan("multisession", workers = n_cores)
  future_map(dvs, function(dv, dat = trials) {

    # Define model formula
    form <- paste0(
      dv, " ~ part * condition +
        (part * condition | subject_id) +
        (part * condition | item_id)"
    ) %>% formula()

    # Define follow-up comparisons
    specs <- pairwise ~ condition | part

    # Fit initial model
    fit <- lmer(form, dat, REML = FALSE)

    # Refit using all available optimizers
    fits <- all_fit(fit, formula = form, data = dat)

    # See which of the optimizers converged
    fits_converged <- keep(
      fits,
      ~ .x@optinfo$conv$opt == 0 &
        length(.x@optinfo$conv$lme4) == 0 &
        length(.x@optinfo$warnings) == 0
    )

    # Find best model via logLik
    logliks <- map(fits_converged, logLik)
    fit_best <- fits[[which.max(logliks)]]

    # Compute follow-up comparisons
    emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
    em <- emmeans(fit_best, specs, infer = TRUE)

    # Return a list of relevant model outputs
    return(
      list(
        fit = fit_best,
        anova = anova(fit_best),
        means = em$emmeans,
        contrasts = em$contrasts,
        all_fits = fits
      )
    )
  }) %>%

    # Save
    set_names(dvs) %T>%
    saveRDS(fnames$models_freq) -> models_freq

  # Stop the workers
  future:::ClusterRegistry("stop")
}

please_stop_here()
```

@@

contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1)))
contrasts_part <- t(cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)))
contrasts(data_brm$condition) <- ginv(contrasts_condition)
contrasts(data_brm$part) <- ginv(contrasts_part)

@@

```{r fig1, include=TRUE, fig.height=11, fig.cap = "(ref:fig1_caption)"}
# Load montage and data
montage <- read_csv(fnames$montage, col_types = cols())
evokeds <- read_csv(fnames$evo_gavg, col_types = cols())

# Create plot for Experiment 1
plot_grid(
  plot_trials(),
  plot_erps(erp_components, evokeds, models_freq, montage),
  nrow = 2, rel_heights = c(5, 6), labels = c("A", "B"), label_fontfamily = "Helvetica"
) + # Add some lines (to separate the parts) and the legend
  annotate_line(x = 0.328, xend = 0.328, y = -Inf, yend = 0.53) +
  annotate_line(x = 0.672, xend = 0.672, y = -Inf, yend = 0.53) +
  annotate_line(x = 0.328, xend = 0.28, y = 0.53, yend = 0.58) +
  annotate_line(x = 0.672, xend = 0.72, y = 0.53, yend = 0.58) +
  annotate_line(x = 0.28, xend = 0.28, y = 0.58, yend = Inf) +
  annotate_line(x = 0.72, xend = 0.72, y = 0.58, yend = Inf) +
  draw_plot(
    plot_legends_erps(direction = "vertical"),
    x = 0.405, y = 0.422, width = 1, height = 1
  )
```

(ref:fig1_caption) Procedure and Results of Experiment 1\smallskip

@@

Offline, the data were preprocessed using the MNE software [Version 0.21.0\; @gramfort2013] in Python [Version 3.8.5\; @vanrossum2009]. First, all scalp electrodes were re-referenced to the common average. Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA). The first 15 components were extracted by the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz. Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the *find\_bads\_eog* function. After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied. Next, the continuous EEG was epoched into segments of 2 s, starting 500 ms before the onset of the visual presentation of each unfamiliar object. The epochs were baseline-corrected by subtracting the average voltage during the 200 ms before stimulus onset. Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis. This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials per participant (= `r percent(mean(rejected_exp1)/360, accuracy = 0.1)`; range `r min(rejected_exp1)` to `r max(rejected_exp1)` trials). Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (for the positions of these electrodes on the scalp, see the topographies in Figure \@ref(fig:exp1-plot)B).

@@

First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded objects from all further analyses when participants classified them as being known in the pre-insight part (i.e., before any keywords were presented). This led to the exclusion of an average of `r format(round(objects_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r percent(objects_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects). Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analysis was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A). Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption. This was the case for an average of `r format(round(objects_exp1["Informed"], 1), nsmall = 1)` objects per participant (= `r percent(objects_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords). Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption. This was the case for an average of `r format(round(objects_exp1["Naive"], 1), nsmall = 1)` objects per participant (= `r percent(objects_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords). Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts. This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any down-stream effects on the subsequent perception of the objects (post-insight part).

@@

```{r, fig3, include=TRUE}
evo_tfr_flat <- read_csv(fnames$evo_tfr_flat, col_types = cols(), progress = FALSE)
evo_tfr_diff <- read_csv(fnames$evo_tfr_diff, col_types = cols(), progress = FALSE)

# Scaling of power in all plots
limits_power <- c(0, 2)

# Time-frequency of interest based on visual inspect
tfoi <- list(tmin = 200, tmax = 400, fmin = 34, fmax = 48)  # Gamma
# tfoi <- list(tmin = 150, tmax = 350, fmin = 14, fmax = 24)  # Beta

standard_text <- element_text(size = 10, color = "black", family = "Helvetica")

plot_tfr_raster <- function(evo_tfr, limits, tmin, tmax, fmin, fmax, label) {
  # Average across electrodes
  evo_tfr %>%
    pivot_longer(-c(part, time, freq), names_to = "electrode", values_to = "power") %>%
    group_by(part, time, freq) %>%
    summarise(power = mean(power), .groups = "drop") %>%
    # Create one raster plot per part
    group_by(part) %>%
    group_map(function(data_part, part) {
      ggplot(data_part, aes(x = time, y = freq, fill = power)) +
        geom_raster() +
        scale_fill_viridis_c(
          limits = limits,
          labels = function(x) x * 100,
          guide = guide_colorbar(
            title = "Power (% change\nfrom baseline)",
            title.position = "left",
            title.theme = element_text(size = 10, color = "black", angle = 90, lineheight = 1),
            title.hjust = 0.5,
            label.theme = element_text(size = 10, color = "black"),
            barheight = unit(4, "cm"),
            ticks = FALSE,
            direction = "vertical"
          ),
          oob = squish
        ) +
        scale_x_continuous(breaks = seq(-100, 700, 200)) +
        coord_cartesian(expand = FALSE) +
        annotate("rect", xmin = tmin, xmax = tmax, ymin = fmin + 1, ymax = fmax + 1, color = "white", fill = NA, linetype = "dotted") +
        annotate("segment", x = 0, xend = 0, y = -Inf, yend = Inf, color = "white", linetype = "dotted") +
        labs(x = "Time (ms)", y = "") +
        theme_minimal() +
        theme(
          legend.position = "none",
          axis.title = standard_text,
          axis.text = standard_text
        )
    }) -> plotlist
  # Add label and axis title to the first plot
  plotlist[[1]] <- plotlist[[1]] + annotate(
    "text",
    x = -100,
    y = 27,
    label = label,
    size = 10 / .pt,
    angle = 90,
    family = "Helvetica",
    color = "white",
    lineheight = 0.9
  ) +
    ylab("Frequency (ms)")
  # Extract legend for another subplot
  current_legend <<- get_legend(plotlist[[1]] + theme(legend.position = "right"))
  plot_grid(plotlist = plotlist, nrow = 1)
}

plot_tfr_topo <- function(evo_tfr, limits, tmin, tmax, fmin, fmax, legend) {
  # Average across times and frequencies of interest
  evo_tfr_diff %>%
    # Select time window and frequencies of interest
    filter(time >= tmin & time <= tmax & freq >= fmin & freq <= fmax) %>%
    # Convert to long format
    pivot_longer(-c(part, time, freq), names_to = "electrode", values_to = "power") %>%
    # Create one topoplot per part
    group_by(part) %>%
    group_map(function(data_part, part) {
      data_part %>%
        group_by(electrode) %>%
        summarise(power = mean(power), .groups = "drop") %>%
        inner_join(montage, by = "electrode") %>%
        eegUtils::topoplot(
          limits = limits,
          palette = "viridis",
          contour = FALSE,
          quantity = "power",
          scaling = 0.5
        ) +
        theme(legend.position = "none",)
    }) -> plotlist
  #plotlist <- c(plotlist, list(legend))
  plot_grid(
    NULL,
    plotlist[[1]],
    NULL,
    plotlist[[2]],
    NULL,
    plotlist[[3]],
    nrow = 1,
    rel_widths = c(2, 7, 0, 7, 1, 7))
}

# Bring it all together
plot_grid(
  plot_headings(spacing = c(1, 7, 1, 7, 1, 7)),
  do.call(
    plot_tfr_raster, c(tfoi, list(
      evo_tfr = evo_tfr_flat,
      limits = limits_power,
      label = "All channels,\nall conditions"
    ))
  ),
  do.call(
    plot_tfr_raster, c(tfoi, list(
      evo_tfr = evo_tfr_diff,
      limits = limits_power,
      label = "All channels,\n\u0394 (informed - naive)"
    ))
  ),
  do.call(
    plot_tfr_topo, c(tfoi, list(
      evo_tfr = evo_tfr_diff,
      limits = limits_power,
      legend = current_legend))
  ),
  nrow = 4,
  rel_heights = c(1, 5, 5, 5),
  labels = c("", "A", "B", "C"),
  label_y = c(1, 1.16, 1.1, 1),
  label_fontfamily = "Helvetica"
) +
  draw_plot(current_legend, x = -0.42, y = -0.34) +
  annotate_line(0.344, 0.344, -Inf, Inf) +
  annotate_line(0.676, 0.676, -Inf, Inf) +
  ggsave("data/processed/tfr.pdf", width = unit(10, "cm"), height = unit(7, "cm"), device = cairo_pdf)
```

@@

# Apply contrasts to the factors in the data
contrasts(data_exp2$condition) <- ginv(contrasts_condition)
contrasts(data_exp2$part) <- ginv(contrasts_part)

@@

```{r exp2-plot, include=TRUE, fig.height=7.5, fig.cap = "(ref:fig2_caption)"}
# Create plot for Experiment 2
plot_grid(
  #plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
  plot_headings(spacing = c(10, 1, 10, 1, 10)),
  plot_erps(comps = comps, evokeds = evokeds_exp2, models = models_exp2, montage = montage),
  plot_legends_erps(direction = "horizontal"),
  nrow = 3, rel_heights = c(0.3, 6, 1.2), labels = NULL
) + # Add some lines (to separate the parts)
  annotate_line(x = 0.328, xend = 0.328, y = 0.15, yend = Inf) +
  annotate_line(x = 0.672, xend = 0.672, y = 0.15, yend = Inf)
```

(ref:fig2_caption) Results of Experiment 2\smallskip

@@

(ref:fig3_caption) Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip
